### 2021-07-14 src/paper/data/policies.tex

Our policies (denoted by $\rho$) usually affect one of three contact types: education,
work and other contacts.
% households
Germany had no policies limiting contacts within households so there are no policies on
them in our model.\footnote{Household contacts can, however, be reduced when individuals
quarantine themselves after developing symptoms, for example. This happens to a lesser
degree than other contacts to capture difficulties in isolation within the home.}
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and rotating schooling
schedules where only one half of students attends every other week or day.
% For the moment we ignore that lack of childcare leads working parents to stay home.
An approximation of the share of contacts still taking place with the different school
regulations can be found in Figure~\ref{fig:school_multiplier}.
% work
For work contacts we use the reductions in work mobility reported by the Google Mobility
Data \citep{Google2021} to calibrate the reduction in physical work contacts
($\rho_{w,\:attend,\:t}$). Reductions in work contacts are not random but governed
through a work contact priority where the policy changes the threshold below which
workers stay home. Figure \ref{fig:work_multiplier} shows the share of workers that go to
work over time at the federal German level. We use the data on the state level to account
for local holidays and differences in state regulations.
% hygiene umltiplier
In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19 ($\rho_{hygiene}$).

>>>>

Our policies (denoted by $\rho$) usually affect one of three contact types: education,
work and other contacts.
% households
Germany had no policies limiting contacts within households so there are no policies on
them in our model.\footnote{Household contacts can, however, be reduced when individuals
quarantine themselves after developing symptoms, for example. This happens to a lesser
degree than other contacts to capture difficulties in isolation within the home.}
% educ models
\input{paper/data/school_policies}

% work
For work contacts we use the reductions in work mobility reported by the Google Mobility
Data \citep{Google2021} to calibrate the reduction in physical work contacts
($\rho_{w,\:attend,\:t}$). Reductions in work contacts are not random but governed
through a work contact priority where the policy changes the threshold below which
workers stay home. Figure \ref{fig:work_multiplier} shows the share of workers that go to
work over time at the federal German level. We use the data on the state level to account
for local holidays and differences in state regulations.
% hygiene umltiplier
In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19 ($\rho_{hygiene}$).
